AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-05 Paper/main.tex

Attention(Q,K,V)=align(Q,K)V\label{eq:12}\vspace*{-10pt}

@@

K_i=Encoder({X_e}_i,\theta_E,K_{i-1})\label{eq:13}
Q_i=Decoder({X_e}_i,\theta_D,Q_{i-1})\label{eq:14}
V=K\label{eq:15}\vspace*{-10pt}

@@

In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 

@@

>>>>

Attention(Q,K,V)=align(Q,K)V\label{eq:13}\vspace*{-10pt}

@@

\left\{\begin{matrix}
K_i=Encoder({X_e}_i,\theta_E,K_{i-1})
\\ Q_i=Decoder({X_e}_i,\theta_D,Q_{i-1})
\\V=K 
\end{matrix}\right.\label{eq:14}\vspace*{-10pt}

@@

@@

Further, if we think of the values matrix as a vector form of the first-order preference $A$ in Equation~(\ref{eq:05}), we can reach the following equation
\tilde{A}=BV\label{eq:19}\vspace*{-10pt}
according to above, values matrix $V$ comes from the hidden states of a bidirectional GRU networks, which is usually hard to understand and explain.
While $B$ is the second-order preference matrix obtained by the attention mechanism, in our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 
